\thesistitle

### 2019-06-26 sections/research.tex
New example for clone graph

\subsubsection{Comparing Statements/Declarations}
In the previous section we described a ``duplicate'' relation between nodes in the clone graph built by CloneRefactor. Whether two nodes in this graph are duplicates of each other is dependent on the clone type. In this section, we will describe for each type how we compare statements and declarations assess whether they are clones of each other.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{img/CodeGraph4}
  \caption{Clone graph with a clone class consisting of three clone instances marked.}
  \label{fig:clonegraph}
\end{figure}

>>>>

\subsubsection{Comparing Statements/Declarations}
In the previous section we described a ``duplicate'' relation between nodes in the clone graph built by CloneRefactor. Whether two nodes in this graph are duplicates of each other is dependent on the clone type. In this section, we will describe for each type how we compare statements and declarations to assess whether they are clones of each other.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{img/CloneGraphCode}
  \caption{CloneRefactor extracts statements and declarations from source code.}
  \label{fig:clonegraph}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{img/CodeGraphExample}
  \caption{Example of a clone graph built by CloneRefactor.}
  \label{fig:clonegraph}
\end{figure}
